---
title: "Lab 00 - Hello IDS!"
author: "Alex"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Zazzie", "Lucy", "Joel", 
           "Gabriel", "Jin", "Alex"),
  github_username = c("zarinakjellberg", "roydsle", "joelhanloned", 
                      "gamgow", "jin2226", "alexjdlr"), 
  colour = c("blue", "darkgreen", "green", 
             "pink", "violet", "red"),
  hobby = c("netball", "reading", "drums", 
            "jazz trumpet", "reading", "cooking"),
  favourite_number = c(2, 7, 2, 4, 2, 10)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


*Remove this text (including the stars), and add your answer for Exercise 18 here.*

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Names", 
          y = "Favourite number",
          title = "Names vs Numbers")
```

*Remove this text (including the stars), and add your answer for Exercise 19 here.*

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Since there are endless answers which are not quantifiable for this question, the data range would be too large to represent tidily with this graph. Maybe using a pie chart would allow us to show the proportion of choices among the study group.
